Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-02-17 main.tex

and further suppose that the classes are balanced ($\pi_0 = \pi_1 = \frac{1}{2}$). We have that the risk of the Bayes decision classifier $C^{A-\mathrm{Bayes}}$ for the projected data $AX$ has a boundary given by $\eta(\mathbf{x}) = 0$ where the function $\eta$ is
$$\eta(\mathbf{x}) = (A\mathbf{x} - \frac{A\mathbf{\mu}_0 + A\mathbf{\mu}_1}{2})^T(A\mu_1 - A\mu_0).$$
We also have that the risk is given by 
$$R(C^{A-\mathrm{Bayes}}) = 1 - \Phi(\frac{1}{2\sigma}(\mu_1 - \mu_0)^TA^TA(\mu_1 - \mu_0)).$$
We can then investigate the quantity 
$$R(C^{A-\mathrm{Bayes}}) - R(C^{A^*-\mathrm{Bayes}}) = \Phi (\frac{1}{2\sigma} |A^*(\mu_1 - \mu_0)|^2) - \Phi(\frac{1}{2\sigma}(|A(\mu_1-\mu_0)|^2),$$
which is bounded below by 
$$\frac{1}{2\sigma}||A(\mu_1 - \mu_0)|^2 - |A^*(\mu_1 - \mu_0)|^2|\phi(\frac{1}{2\sigma}|A^*(\mu_1 - \mu_0)|^2). $$
Rearranging and noting that $A^* = (\mu_1 - \mu_0)/|\mu_1 - \mu_0|$ (up to sign), we can say if given a bound of the form $R(C^{A-\mathrm{Bayes}}) - R(C^{A^*-\mathrm{Bayes}}) < \varepsilon$ that 
$$|A{A^*}^T| \geq \sqrt{1 - \varepsilon \frac{2\sqrt{2\pi}\sigma\exp(\frac{1}{4\sigma^2}|\mu_1 - \mu_0|^4)}{|\mu_1 - \mu_0|^2}}. $$
We notice here that the bound grows weak quickly as the distance between $\mu_0$ and $\mu_1$ increases. This stands to reason, since when signal is clearer projections a long way from optimal may produce good classifiers. The 
\section{Simulations}
\subsection{Case 1: Simple Separation}
We consider the setup
$$X\ | \ Y = 0 \sim N_p(\mathbf{\mu}_0, \Sigma_0) $$
$$X\ | \ Y= 1 \sim N_p(\mathbf{\mu}_1, \Sigma_1) $$
where $\mathbf{\mu}_0 = (1, 0, \dots, 0)$, $\mathbf{\mu}_1 = (-1, 0, \dots, 0)$, $\Sigma_0 = \mathrm{diag}(1, 1, \dots, 1) \ (= I_p)$ and $\Sigma_1 = \mathrm{diag}(1, \lambda, 1, \dots, 1)$. In the simulation shown $\lambda = 0.2$. We see in Figure \ref{fig:simpleboundary} the relatively simple class boundary, mostly dependent upon the value of the first component. We set $p = 100$ so that there are 98 noise components.

@@

\subsection{Case 2: Complex Separation}
\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexboundary.png}
        \caption{}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexeigs.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexfirst.png}
        \caption{}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexsecond.png}
        \caption{}
    \end{subfigure}
\caption{}
\end{figure*}
\section{Real-World Examples}
\subsection{Epilepsy Dataset}

>>>>

and further suppose that the classes are balanced ($\pi_0 = \pi_1 = \frac{1}{2}$). We have that the risk of the Bayes decision classifier $C^{A-\mathrm{Bayes}}$ for the projected data $AX$ has a boundary given by $\eta(\mathbf{x}) = 0$ where the function $\eta$ is
$$\eta(\mathbf{x}) = (A\mathbf{x} - \frac{A\mathbf{\mu}_0 + A\mathbf{\mu}_1}{2})^T(A\mu_1 - A\mu_0).$$
We also have that the risk is given by 
$$R(C^{A-\mathrm{Bayes}}) = 1 - \Phi(\frac{1}{2\sigma}(\mu_1 - \mu_0)^TA^TA(\mu_1 - \mu_0)).$$
We can then investigate the quantity 
$$R(C^{A-\mathrm{Bayes}}) - R(C^{A^*-\mathrm{Bayes}}) = \Phi (\frac{1}{2\sigma} |A^*(\mu_1 - \mu_0)|^2) - \Phi(\frac{1}{2\sigma}(|A(\mu_1-\mu_0)|^2),$$
which is bounded below by 
$$\frac{1}{2\sigma}||A(\mu_1 - \mu_0)|^2 - |A^*(\mu_1 - \mu_0)|^2|\phi(\frac{1}{2\sigma}|A^*(\mu_1 - \mu_0)|^2). $$
Rearranging and noting that $A^* = (\mu_1 - \mu_0)/|\mu_1 - \mu_0|$ (up to sign), we can say if given a bound of the form $R(C^{A-\mathrm{Bayes}}) - R(C^{A^*-\mathrm{Bayes}}) < \varepsilon$ that 
$$|A{A^*}^T| \geq \sqrt{1 - \varepsilon \frac{2\sqrt{2\pi}\sigma\exp(\frac{1}{4\sigma^2}|\mu_1 - \mu_0|^4)}{|\mu_1 - \mu_0|^2}}. $$
We notice here that the bound grows weak quickly as the distance between $\mu_0$ and $\mu_1$ increases. This stands to reason, since when signal is clearer projections a long way from optimal may produce good classifiers. The

\section{Simulations}

\subsection{Sparse class boundaries}
We consider the setup
$$X\ | \ Y = 0 \sim N_p(\mathbf{\mu}_0, \Sigma_0) $$
$$X\ | \ Y= 1 \sim N_p(\mathbf{\mu}_1, \Sigma_1) $$
where $\mathbf{\mu}_0 = (1, 0, \dots, 0)$, $\mathbf{\mu}_1 = (-1, 0, \dots, 0)$, $\Sigma_0 = \mathrm{diag}(1, 1, \dots, 1) \ (= I_p)$ and $\Sigma_1 = \mathrm{diag}(1, \lambda, 1, \dots, 1)$. In the simulation shown $\lambda = 0.2$. We see in Figure \ref{fig:simpleboundary} the relatively simple class boundary, mostly dependent upon the value of the first component. We set $p = 100$ so that there are 98 noise components.

@@

\subsection{Rotated sparse normal}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexboundary.png}
        \caption{}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexeigs.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexfirst.png}
        \caption{}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexsecond.png}
        \caption{}
    \end{subfigure}
\caption{}
\end{figure*}

\subsection{Independent features}

\subsection{$t$‐distributed features}

\section{Real-World Examples}

\subsection{Epilepsy Dataset}
